---
title: "Kenji T. Hayashi"
subtitle: "*Curriculum Vitae*"
format: 
  html: 
    theme:
      - lumen
      - custom.scss
execute: 
  echo: false
  output: asis
---

```{r setup}
library(qmdcv)
library(yaml)

d <- read_yaml("data.yaml")
```

```{r footer}
# Update data in footer by modifying custom.scss
f <- "custom.scss"
s <- readLines(f)
dl <- intersect(grep("date-here", s), grep("content:*", s))
s[dl] <- gsub("(?<=content: )([^;]+)", 
              paste0('"', format(Sys.Date(), "%m/%d/%Y"), '"'), 
              s[dl], 
              perl = TRUE)
writeLines(s, f)
```

:::{style="text-align:center;"}
Ph.D Candidate    
Department of Ecology and Evolutionary Biology    
University of California, Los Angeles   
Email: [kthayashi@ucla.edu](mailto:kthayashi@ucla.edu) | Web: [kthayashi.github.io](https://kthayashi.github.io)
:::

## EDUCATION

```{r education}
education <- d$education
insert(education)
```

## FUNDING

### Grants

```{r grants}
grants <- d$grants
insert(grants)
```

### Fellowships & Scholarships

```{r fellowships}
fellowships <- d$fellowships
insert(fellowships)
```

## HONORS & AWARDS

```{r honors}
honors <- d$honors
insert(honors)
```

::::::{.group}
## PUBLICATIONS

### Journal Articles

:::{.small}
\* indicates equal contribution
:::
::::::

```{r articles}
articles <- d$publications$articles
insert_pubs(articles)
```

:::{.group}
## PRESENTATIONS

### Invited Presentations
:::

```{r}
talks_invited <- d$talks$invited
insert_talks(talks_invited)
```

### Contributed Presentations

```{r}
talks_contributed <- d$talks$contributed
insert_talks(talks_contributed)
```

:::{.group}
## TEACHING & MENTORING

### Teaching Assistantships

#### University of California, Los Angeles
:::

```{r}
TA_UCLA <- d$teaching$TA$UCLA
insert_list(TA_UCLA)
```

#### Brown University

```{r}
TA_Brown <- d$teaching$TA$Brown
insert_list(TA_Brown)
```

### Guest Lectures

```{r}
guest_lectures <- d$teaching$guest_lectures
insert_list(guest_lectures)
```

:::{.group}
### Workshops

```{r}
workshops <- d$teaching$workshops
insert_list(workshops)
```
:::

:::{.group}
### Mentorship

#### Undergraduate Students

```{r}
mentorship_undergrads <- d$teaching$mentorship$undergrads
insert_list(mentorship_undergrads)
```
:::

#### Other

```{r}
mentorship_other <- d$teaching$mentorship$other
insert_list(mentorship_other)
```

### Teaching Certifications

```{r}
teaching_certifications <- d$teaching$certifications
insert_list(teaching_certifications)
```

## OTHER RESEARCH EXPERIENCE

```{r}
research <- d$research
insert(research)
```

:::{.group}
## PUBLIC & PROFESSIONAL SERVICE

### Outreach
:::

```{r}
outreach <- d$service$outreach
insert_list(outreach)
```

### Departmental Service

```{r}
dept_service <- d$service$dept
insert_list(dept_service)
```

### Peer Review

```{r}
peer_review <- d$service$peer_review
insert_list(peer_review)
```

### Professional Associations

```{r}
prof_associations <- d$service$associations
insert_list(prof_associations)
```
