---
title: "Kenji T. Hayashi"
subtitle: "*Curriculum Vitae*"
---

```{r}
#| label: setup

library(qmdcv)
library(yaml)
```

:::{style="text-align:center;"}
Postdoctoral Associate  
Department of BioSciences, Rice University  
Email: [kenji.hayashi@rice.edu](mailto:kenji.hayashi@rice.edu) |
Web: [kthayashi.github.io](https://kthayashi.github.io)
:::

## POSITIONS

```{r}
#| label: positions

positions <- read_yaml("content/positions.yml")
insert(positions)
```

## EDUCATION

```{r}
#| label: education

education <- read_yaml("content/education.yml")
insert(education)
```

## FUNDING

### Grants

```{r}
#| label: grants

grants <- read_yaml("content/grants.yml")
insert(grants)
```

### Fellowships & Scholarships

```{r}
#| label: fellowships

fellowships <- read_yaml("content/fellowships.yml")
insert(fellowships)
```

## HONORS & AWARDS

```{r}
#| label: honors

honors <- read_yaml("content/honors.yml")
insert(honors)
```

## PUBLICATIONS

[\* indicates equal contribution]{.small}

```{r}
#| label: publications

publications <- read_yaml("content/publications.yml")
insert_publications(publications)
```

## PRESENTATIONS

```{r}
#| label: presentations

presentations <- read_yaml("content/presentations.yml")
```

### Invited Presentations

```{r}
#| label: invited-presentations

insert_presentations(presentations$invited)
```

### Contributed Presentations

```{r}
#| label: contributed-presentations

insert_presentations(presentations$contributed)
```

## TEACHING & MENTORING

```{r}
#| label: teaching

teaching <- read_yaml("content/teaching.yml")
```

### Teaching Assistantships

#### University of California, Los Angeles

```{r}
#| label: TA-UCLA

insert_list(teaching$TA$UCLA)
```

#### Brown University

```{r}
#| label: TA-Brown

insert_list(teaching$TA$Brown)
```

### Guest Lectures

```{r}
#| label: guest-lectures

insert_list(teaching$guest_lectures)
```

### Workshops

```{r}
#| label: workshops

insert_list(teaching$workshops)
```

### Mentorship

#### Undergraduate Students

```{r}
#| label: mentorship-undergrads

insert_list(teaching$mentorship$undergrads)
```

#### Other

```{r}
#| label: mentorship-other

insert_list(teaching$mentorship$other)
```

### Certifications

```{r}
#| label: certifications

insert_list(teaching$certifications)
```

## OTHER RESEARCH EXPERIENCE

```{r}
#| label: other

other <- read_yaml("content/other.yml")
insert(other)
```

## PUBLIC & PROFESSIONAL SERVICE

```{r}
#| label: service

service <- read_yaml("content/service.yml")
```

### Outreach

```{r}
#| label: outreach

insert_list(service$outreach)
```

### Departmental Service

```{r}
#| label: dept-service

insert_list(service$dept)
```

### Peer Review

```{r}
#| label: peer-review

insert_list(service$peer_review)
```

### Professional Associations

```{r}
#| label: professional-associations

insert_list(service$associations)
```
